Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-25 paper/ms.tex
fixed references into main file. fixed keywords

\begin{abstract}
We study the impact of cosmic variance and observational uncertainties
in constraining the mass and occupation fraction, \focc, of
dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
We construct mock catalogs from an N-body simulation to match the 
typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
In our model a dark matter halo with mass in the range $\mmin
<M_{\mathrm h}<\mmax$ can only host one detectable LAEat most.    
We explore the parameter space determined by \mmin, \mmax\ and \focc\
with a Markov Chain Monte-Carlo algorithm using as observational
constraints the angular correlation function (ACF) and the LAEs number density. 
We find that the preferred minium and maximum masses in our model span
a wide range $10^{9.6}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
$10^{10.9}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
As a consequence the median mass, $M_{50}$, of all models consistent with
observations has a large uncertainty $M_{50} =
3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun, in agreement with the most recent
observational estimates.
However, we find that the same individual models have a relatively tight
mass gap, $\Delta M \equiv \log_{10}\mmax - \log_{10}\mmin$, of $\Delta
M\approx 0.3$dex.
We are also able show that \focc\ is uniquely determined by $M_{\rm
  min}$, regardless of $M_{\rm max}$, by
$\focc\sim0.1(\mmin/10^{10.5}\hMsun )^{0.93}$.  
However, the current observational data only allows us to put weak
constraints on \mmin\ and consequently on \focc.
We argue that upcoming large surveys covering at least $25$ deg$^{2}$
should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
distribution width, $W_{1\sigma}$, constructed over several fields of
$\sim 1$ deg$^{2}$ using the relationship, $W_{1\sigma} =
0.138\times (\mmin/10^{11}\hMsun )^{0.177}$, calibrated from our results.
\end{abstract}

\keywords{
Cosmology: theory - large-scale structure of Universe -
Methods: data analysis - numerical - N-body simulations
}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{fig1.pdf}
\caption{Cumulative halo number density distribution function over
  27 mock fields. Each line corresponds to a
  different model with increasig values of $M_{\rm min}$. 
  Different models produce different number density distributions. The
width of the distribution increases with \mmin. } 
\label{fig:cosmicv0}
\end{figure}

@@

Nevertheless, our analysis allowed us to draw three results that can
be used to put tighter constraints on \mmin, \mmax and \focc once
upcoming large LAE surveys, such as the HETDEX project 
\citep{Hetdex2011} and the HSC ultra deep survey, are available: 
\begin{enumerate}
\item \focc is uniquely determined by \mmin, regardless of
  \mmax. A precise determination of \mmin\ will thus fix \focc. As a consequence of this, for a given  \mmin the media mass is also  fixed.

\item ALSO MENTION THIS HERE BECAUSE IS A STRONG CONSTRAIN:
 the 1-$\sigma$ width of the mass distribution is highly constrained to be between $0.2$ and $0.6$ dex. SOMETHING THAT IS ALSO IMPORTANT IS THAT THIS CONSTRAIN IS ASSUMING OUR MODEL IS RIGHT, IF IT HAPPENS TO BE THAT THE FUNCTION THAT RELATES LUMINOSITY WITH MASS IS VERY STEPPEN THEN THE RESULTS MAY CHANGE.

\item The width of the LAE number distribution function
  obtained over several fields of $\approx 1$ deg$^2$ is tightly
  correlated with \mmin. That measurement with next generation surveys
  will be able to constrain \mmin within a factor of $\sim 2$.
\item The ACF becomes slightly stronger at short angular
  distances ($<1\,\rm arcmin$) when \mmax\ increases therefore precise
 measurements of the  ACF at such scales are crucial to accurately
 determine \mmax.  
\end{enumerate}

@@

\bibliographystyle{apj}
\bibliography{references.bib}

>>>>

\begin{abstract}
We study the impact of cosmic variance and observational uncertainties
in constraining the mass and occupation fraction, \focc, of
dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
We construct mock catalogs from an N-body simulation to match the 
typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
In our model a dark matter halo with mass in the range $\mmin
<M_{\mathrm h}<\mmax$ can only host one detectable LAEat most.    
We explore the parameter space determined by \mmin, \mmax\ and \focc\
with a Markov Chain Monte-Carlo algorithm using as observational
constraints the angular correlation function (ACF) and the LAEs number density. 
We find that the preferred minium and maximum masses in our model span
a wide range $10^{9.6}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
$10^{10.9}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
As a consequence the median mass, $M_{50}$, of all models consistent with
observations has a large uncertainty $M_{50} =
3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun, in agreement with the most recent
observational estimates.
However, we find that the same individual models have a relatively tight
$1\sigma$ mass gap $\Delta M_{1\sigma}\approx 0.4$ dex.
We are also able show that \focc\ is uniquely determined by $M_{\rm
  min}$, regardless of $M_{\rm max}$. 
We argue that upcoming large surveys covering at least $25$ deg$^{2}$
should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
distribution width, $W_{1\sigma}$, constructed over several fields of
$\sim 1$ deg$^{2}$.
\end{abstract}

\keywords{
Galaxies: halos --- Galaxies: high-redshift --- Galaxies: statistics
--- Dark Matter --- Methods: numerical 
}

@@

\begin{figure}
\includegraphics[width=0.47\textwidth]{fig1.pdf}
\caption{Cumulative halo number density distribution function over
  27 mock fields. Each line corresponds to a
  different model with increasig values of \mmin. 
  Different models produce different number density distributions. 
  The width of the distribution increases with \mmin. } 
\label{fig:cosmicv0}
\end{figure}

@@

Nevertheless, our analysis allowed us to draw three results that can
be used to put tighter constraints on \mmin and \focc once
upcoming large LAE surveys, such as the HETDEX project 
\citep{Hetdex2011} and the HSC ultra deep survey, are available:

\begin{enumerate}
\item \focc is uniquely determined by \mmin, regardless of
  \mmax. A precise determination of \mmin\ will thus fix \focc. As a consequence of this, for a given  \mmin the media mass is also  fixed.

\item The width of the LAE number distribution function
  obtained over several fields of $\approx 1$ deg$^2$ is tightly
  correlated with \mmin. That measurement with next generation surveys
  will be able to constrain \mmin within a factor of $\sim 2$.

We also find that the 1-$\sigma$ width of the mass distribution is
highly constrained to be between $0.2$ and $0.6$ dex. 
This result imposes constraints on different models for LAEs formation
in a cosmological context as to why observable LAEs are constrained
into a narrow halo mass range.

Overall, our approach highlights the importance of forward modelling
to take explicitly into account the effects of cosmic variance.
We expect this

\end{enumerate}

@@

\bibliographystyle{apj}
%\bibliography{references.bib}
\begin{thebibliography}{38}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Adams} {et~al.}(2011){Adams}, {Blanc}, {Hill}, {Gebhardt}, {Drory},
  {Hao}, {Bender}, {Byun}, {Ciardullo}, {Cornell}, {Finkelstein}, {Fry},
  {Gawiser}, {Gronwall}, {Hopp}, {Jeong}, {Kelz}, {Kelzenberg}, {Komatsu},
  {MacQueen}, {Murphy}, {Odoms}, {Roth}, {Schneider}, {Tufts}, \&
  {Wilkinson}}]{Hetdex2011}
{Adams}, J.~J., {Blanc}, G.~A., {Hill}, G.~J., {Gebhardt}, K., {Drory}, N.,
  {Hao}, L., {Bender}, R., {Byun}, J., {Ciardullo}, R., {Cornell}, M.~E.,
  {Finkelstein}, S.~L., {Fry}, A., {Gawiser}, E., {Gronwall}, C., {Hopp}, U.,
  {Jeong}, D., {Kelz}, A., {Kelzenberg}, R., {Komatsu}, E., {MacQueen}, P.~J.,
  {Murphy}, J., {Odoms}, P.~S., {Roth}, M., {Schneider}, D.~P., {Tufts}, J.~R.,
  \& {Wilkinson}, C.~P. 2011, \apjs, 192, 5

\bibitem[{{Behroozi} {et~al.}(2013){Behroozi}, {Wechsler}, \&
  {Conroy}}]{Behroozi2013a}
{Behroozi}, P.~S., {Wechsler}, R.~H., \& {Conroy}, C. 2013, \apj, 770, 57

\bibitem[{{Bielby} {et~al.}(2016){Bielby}, {Tummuangpak}, {Shanks}, {Francke},
  {Crighton}, {Ba{\~n}ados}, {Gonz{\'a}lez-L{\'o}pez}, {Infante}, \&
  {Orsi}}]{Bielby16}
{Bielby}, R.~M., {Tummuangpak}, P., {Shanks}, T., {Francke}, H., {Crighton},
  N.~H.~M., {Ba{\~n}ados}, E., {Gonz{\'a}lez-L{\'o}pez}, J., {Infante}, L., \&
  {Orsi}, A. 2016, \mnras, 456, 4061

\bibitem[{{Blanc} {et~al.}(2011){Blanc}, {Adams}, {Gebhardt}, {Hill}, {Drory},
  {Hao}, {Bender}, {Ciardullo}, {Finkelstein}, {Fry}, {Gawiser}, {Gronwall},
  {Hopp}, {Jeong}, {Kelzenberg}, {Komatsu}, {MacQueen}, {Murphy}, {Roth},
  {Schneider}, \& {Tufts}}]{Blanc11}
{Blanc}, G.~A., {Adams}, J.~J., {Gebhardt}, K., {Hill}, G.~J., {Drory}, N.,
  {Hao}, L., {Bender}, R., {Ciardullo}, R., {Finkelstein}, S.~L., {Fry}, A.~B.,
  {Gawiser}, E., {Gronwall}, C., {Hopp}, U., {Jeong}, D., {Kelzenberg}, R.,
  {Komatsu}, E., {MacQueen}, P., {Murphy}, J.~D., {Roth}, M.~M., {Schneider},
  D.~P., \& {Tufts}, J. 2011, \apj, 736, 31

\bibitem[{{Bond} {et~al.}(2009){Bond}, {Gawiser}, {Gronwall}, {Ciardullo},
  {Altmann}, \& {Schawinski}}]{Bond2009}
{Bond}, N.~A., {Gawiser}, E., {Gronwall}, C., {Ciardullo}, R., {Altmann}, M.,
  \& {Schawinski}, K. 2009, \apj, 705, 639

\bibitem[{{Colberg} {et~al.}(2000){Colberg}, {White}, {Yoshida}, {MacFarland},
  {Jenkins}, {Frenk}, {Pearce}, {Evrard}, {Couchman}, {Efstathiou}, {Peacock},
  {Thomas}, \& {Virgo Consortium}}]{Colberg00}
{Colberg}, J.~M., {White}, S.~D.~M., {Yoshida}, N., {MacFarland}, T.~J.,
  {Jenkins}, A., {Frenk}, C.~S., {Pearce}, F.~R., {Evrard}, A.~E., {Couchman},
  H.~M.~P., {Efstathiou}, G., {Peacock}, J.~A., {Thomas}, P.~A., \& {Virgo
  Consortium}. 2000, \mnras, 319, 209

\bibitem[{{Dayal} {et~al.}(2009){Dayal}, {Ferrara}, {Saro}, {Salvaterra},
  {Borgani}, \& {Tornatore}}]{Dayal2009}
{Dayal}, P., {Ferrara}, A., {Saro}, A., {Salvaterra}, R., {Borgani}, S., \&
  {Tornatore}, L. 2009, \mnras, 400, 2000

\bibitem[{{Dijkstra}(2014)}]{Dijkstra14}
{Dijkstra}, M. 2014, \pasa, 31, e040

\bibitem[{{Dijkstra} \& {Kramer}(2012)}]{Dijkstra2012}
{Dijkstra}, M., \& {Kramer}, R. 2012, \mnras, 424, 1672

\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
  {Goodman}}]{emcee2013}
{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
  125, 306

\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Yepes},
  {Gottl{\"o}ber}, {Knollmann}, {Cuesta}, \& {Prada}}]{ForeroRomero2011}
{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., {Knollmann}, S.~R.,
  {Cuesta}, A.~J., \& {Prada}, F. 2011, \mnras, 415, 3666

\bibitem[{{Forero-Romero} {et~al.}(2012){Forero-Romero}, {Yepes},
  {Gottl{\"o}ber}, \& {Prada}}]{ForeroRomero2012}
{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., \& {Prada}, F. 2012,
  \mnras, 419, 952

\bibitem[{{Garel} {et~al.}(2012){Garel}, {Blaizot}, {Guiderdoni}, {Schaerer},
  {Verhamme}, \& {Hayes}}]{Garel2012}
{Garel}, T., {Blaizot}, J., {Guiderdoni}, B., {Schaerer}, D., {Verhamme}, A.,
  \& {Hayes}, M. 2012, \mnras, 422, 310

\bibitem[{{Gawiser} {et~al.}(2007{\natexlab{a}}){Gawiser}, {Francke}, {Lai},
  {Schawinski}, {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos},
  {Blanc}, {Fazio}, \& {Feldmeier}}]{Gawiser2007}
{Gawiser}, E., {Francke}, H., {Lai}, K., {Schawinski}, K., {Gronwall}, C.,
  {Ciardullo}, R., {Quadri}, R., {Orsi}, A., {Barrientos}, L.~F., {Blanc},
  G.~A., {Fazio}, G., \& {Feldmeier}, J.~J. 2007{\natexlab{a}}, \apj, 671, 278

\bibitem[{{Gawiser} {et~al.}(2007{\natexlab{b}}){Gawiser}, {Francke}, {Lai},
  {Schawinski}, {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos},
  {Blanc}, {Fazio}, {Feldmeier}, {Huang}, {Infante}, {Lira}, \&
  {Padilla}}]{Gawiser07}
{Gawiser}, E., {Francke}, H., {Lai}, K., {Schawinski}, K., {Gronwall}, C.,
  {Ciardullo}, R., {Quadri}, R., {Orsi}, A., {Barrientos}, L.~F., {Blanc},
  G.~A., {Fazio}, G., {Feldmeier}, J.~J., {Huang}, J.-s., {Infante}, L.,
  {Lira}, P., \& {Padilla}, N. 2007{\natexlab{b}}, \apj, 671, 278

\bibitem[{{Hayashino} {et~al.}(2004){Hayashino}, {Matsuda}, {Tamura},
  {Yamauchi}, {Yamada}, {Ajiki}, {Fujita}, {Murayama}, {Nagao}, {Ohta},
  {Okamura}, {Ouchi}, {Shimasaku}, {Shioya}, \& {Taniguchi}}]{Hayashino2004}
{Hayashino}, T., {Matsuda}, Y., {Tamura}, H., {Yamauchi}, R., {Yamada}, T.,
  {Ajiki}, M., {Fujita}, S.~S., {Murayama}, T., {Nagao}, T., {Ohta}, K.,
  {Okamura}, S., {Ouchi}, M., {Shimasaku}, K., {Shioya}, Y., \& {Taniguchi}, Y.
  2004, \aj, 128, 2073

\bibitem[{{Hayes}(2015)}]{Hayes15}
{Hayes}, M. 2015, \pasa, 32, e027

\bibitem[{{Jose} {et~al.}(2013){Jose}, {Srianand}, \&
  {Subramanian}}]{Jose2013b}
{Jose}, C., {Srianand}, R., \& {Subramanian}, K. 2013, ArXiv e-prints

\bibitem[{{Klypin} {et~al.}(2014){Klypin}, {Yepes}, {Gottlober}, {Prada}, \&
  {Hess}}]{BolshoiP}
{Klypin}, A., {Yepes}, G., {Gottlober}, S., {Prada}, F., \& {Hess}, S. 2014,
  ArXiv e-prints

\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
  {Primack}}]{Bolshoi}
{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102

\bibitem[{{Koehler} {et~al.}(2007){Koehler}, {Schuecker}, \&
  {Gebhardt}}]{Koehler2007}
{Koehler}, R.~S., {Schuecker}, P., \& {Gebhardt}, K. 2007, \aap, 462, 7

\bibitem[{{Landy} \& {Szalay}(1993)}]{Landy1993}
{Landy}, S.~D., \& {Szalay}, A.~S. 1993, \apj, 412, 64

\bibitem[{{Laursen} {et~al.}(2013){Laursen}, {Duval}, \&
  {{\"O}stlin}}]{Laursen2013}
{Laursen}, P., {Duval}, F., \& {{\"O}stlin}, G. 2013, \apj, 766, 124

\bibitem[{{Laursen} \& {Sommer-Larsen}(2007)}]{Laursen2007}
{Laursen}, P., \& {Sommer-Larsen}, J. 2007, \apjl, 657, L69

\bibitem[{{Neufeld}(1991)}]{Neufeld1991}
{Neufeld}, D.~A. 1991, \apjl, 370, L85

\bibitem[{{Nilsson} {et~al.}(2007){Nilsson}, {M{\o}ller}, {M{\"o}ller},
  {Fynbo}, {Micha{\l}owski}, {Watson}, {Ledoux}, {Rosati}, {Pedersen}, \&
  {Grove}}]{Nilsson2007}
{Nilsson}, K.~K., {M{\o}ller}, P., {M{\"o}ller}, O., {Fynbo}, J.~P.~U.,
  {Micha{\l}owski}, M.~J., {Watson}, D., {Ledoux}, C., {Rosati}, P.,
  {Pedersen}, K., \& {Grove}, L.~F. 2007, \aap, 471, 71

\bibitem[{{Orsi} {et~al.}(2012){Orsi}, {Lacey}, \& {Baugh}}]{Orsi2012}
{Orsi}, A., {Lacey}, C.~G., \& {Baugh}, C.~M. 2012, \mnras, 425, 87

\bibitem[{{Ouchi} {et~al.}(2008){Ouchi}, {Shimasaku}, {Akiyama}, {Simpson},
  {Saito}, {Ueda}, {Furusawa}, {Sekiguchi}, {Yamada}, {Kodama}, {Kashikawa},
  {Okamura}, {Iye}, {Takata}, {Yoshida}, \& {Yoshida}}]{Ouchi2008}
{Ouchi}, M., {Shimasaku}, K., {Akiyama}, M., {Simpson}, C., {Saito}, T.,
  {Ueda}, Y., {Furusawa}, H., {Sekiguchi}, K., {Yamada}, T., {Kodama}, T.,
  {Kashikawa}, N., {Okamura}, S., {Iye}, M., {Takata}, T., {Yoshida}, M., \&
  {Yoshida}, M. 2008, \apjs, 176, 301

\bibitem[{{Ouchi} {et~al.}(2010){Ouchi}, {Shimasaku}, {Furusawa}, {Saito},
  {Yoshida}, {Akiyama}, {Ono}, {Yamada}, {Ota}, {Kashikawa}, {Iye}, {Kodama},
  {Okamura}, {Simpson}, \& {Yoshida}}]{Ouchi2010}
{Ouchi}, M., {Shimasaku}, K., {Furusawa}, H., {Saito}, T., {Yoshida}, M.,
  {Akiyama}, M., {Ono}, Y., {Yamada}, T., {Ota}, K., {Kashikawa}, N., {Iye},
  M., {Kodama}, T., {Okamura}, S., {Simpson}, C., \& {Yoshida}, M. 2010, \apj,
  723, 869

\bibitem[{{Partridge} \& {Peebles}(1967)}]{Partridge67}
{Partridge}, R.~B., \& {Peebles}, P.~J.~E. 1967, \apj, 147, 868

\bibitem[{{Peebles}(1980)}]{Peebles1980}
{Peebles}, P.~J.~E. 1980, {The large-scale structure of the universe}

\bibitem[{{Planck Collaboration} {et~al.}(2014){Planck Collaboration}, {Ade},
  {Aghanim}, {Armitage-Caplan}, {Arnaud}, {Ashdown}, {Atrio-Barandela},
  {Aumont}, {Baccigalupi}, {Banday}, \& et~al.}]{Planck2014}
{Planck Collaboration}, {Ade}, P.~A.~R., {Aghanim}, N., {Armitage-Caplan}, C.,
  {Arnaud}, M., {Ashdown}, M., {Atrio-Barandela}, F., {Aumont}, J.,
  {Baccigalupi}, C., {Banday}, A.~J., \& et~al. 2014, \aap, 571, A16

\bibitem[{{Rhoads} {et~al.}(2000){Rhoads}, {Malhotra}, {Dey}, {Stern},
  {Spinrad}, \& {Jannuzi}}]{Rhoads00}
{Rhoads}, J.~E., {Malhotra}, S., {Dey}, A., {Stern}, D., {Spinrad}, H., \&
  {Jannuzi}, B.~T. 2000, \apjl, 545, L85

\bibitem[{Riebe {et~al.}(2013)Riebe, Partl, Enke, Forero-Romero, Gottlöber,
  Klypin, Lemson, Prada, Primack, Steinmetz, \& Turchaninov}]{MultiDark}
Riebe, K., Partl, A.~M., Enke, H., Forero-Romero, J., Gottlöber, S., Klypin,
  A., Lemson, G., Prada, F., Primack, J.~R., Steinmetz, M., \& Turchaninov, V.
  2013, Astronomische Nachrichten, 334, 691

\bibitem[{{Springel} {et~al.}(2005){Springel}, {White}, {Jenkins}, {Frenk},
  {Yoshida}, {Gao}, {Navarro}, {Thacker}, {Croton}, {Helly}, {Peacock}, {Cole},
  {Thomas}, {Couchman}, {Evrard}, {Colberg}, \& {Pearce}}]{SpringelNature05}
{Springel}, V., {White}, S.~D.~M., {Jenkins}, A., {Frenk}, C.~S., {Yoshida},
  N., {Gao}, L., {Navarro}, J., {Thacker}, R., {Croton}, D., {Helly}, J.,
  {Peacock}, J.~A., {Cole}, S., {Thomas}, P., {Couchman}, H., {Evrard}, A.,
  {Colberg}, J., \& {Pearce}, F. 2005, \nat, 435, 629

\bibitem[{{Verhamme} {et~al.}(2006){Verhamme}, {Schaerer}, \&
  {Maselli}}]{Verhamme2006}
{Verhamme}, A., {Schaerer}, D., \& {Maselli}, A. 2006, \aap, 460, 397

\bibitem[{{Yajima} {et~al.}(2012){Yajima}, {Choi}, \& {Nagamine}}]{Yajima2012}
{Yajima}, H., {Choi}, J.-H., \& {Nagamine}, K. 2012, \mnras, 427, 2889

\bibitem[{{Yajima} {et~al.}(2014){Yajima}, {Li}, {Zhu}, {Abel}, {Gronwall}, \&
  {Ciardullo}}]{Yajima14}
{Yajima}, H., {Li}, Y., {Zhu}, Q., {Abel}, T., {Gronwall}, C., \& {Ciardullo},
  R. 2014, \mnras, 440, 776

\end{thebibliography}
